\LaTeX\ Author Guidelines for ICCV Proceedings

### 2020-03-10 chapters/3_algorithm.tex
Update to ECCV template

\begin{figure}
\centering
        \begin{subfigure}[t]{0.42 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \\\vspace{8pt}
    \begin{subfigure}[t]{0.42 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
        \caption{With cannot-link constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. The edge selected at each iteration is highlighted in yellow. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}

% \begin{table*}[t]
%     % \centering
%     \scriptsize
%     \begin{subtable}[t!]{0.6\textwidth}\centering
%         \begin{tabular}{r  l | c | c  c}
%             \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
%             \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\

%             \midrule
%              Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\

%              \makecell[r]{Abs. Max:} & 
%             $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
%                & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
%              \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\

%             Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\

%             Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}

%         \end{tabular}
%     \end{subtable} 
%     \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
%     \label{tab:linkage-criteria}
% \end{table*}

\begin{table*}[t]
    \centering
    \footnotesize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{c | c  c  c  c  c}
        \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  & Sum & Absolute Maximum & Average & Maximum & Minimum \\
 & $\displaystyle \sum_{e\in E_{uv}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big| $ &  $\displaystyle \max_{e\in E_{uv}} \cost_e$ & $\displaystyle \min_{e\in E_{uv}} \cost_e$ \\ \midrule

            \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Average Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Complete Linkage\\Hier. Aggl. Clust.} \\
            \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
            \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
            % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule

            %  Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\

            %  \makecell[r]{Abs. Max:} & 
            % $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
            %    & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\

            %  \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\

            % Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\

            % Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}

        \end{tabular}
    \end{subtable} 
    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}

\begin{figure*}
\centering
\includegraphics[width=0.96\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. Only the \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
\label{fig:cremi_comparison}}
\end{figure*}

>>>>

\begin{figure}[t]
\centering
        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/example_no_constr.pdf}
        \caption{No constraints}\label{subfig:no_constraints}
    \end{subfigure} \hfill \vspace{8pt}
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/example_with_constr.pdf}
        \caption{With cannot-link constraints}\label{subfig:with_constraints}
    \end{subfigure}
\caption{Some iterations of the generalized algorithm (using \emph{Sum} linkage criteria) with and without adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges and cannot-link constraints are shown with triple violet bars on the edges. The edge selected at each iteration is highlighted in yellow. We note that when constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}
\end{figure}

\begin{table*}[t]
    % \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{R{5em}  l | M{10em} | M{8em}  M{8em}}
            \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria}\\ $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned} \\\textbf{Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
            \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No \\Constraints}} & \thead{With\\ Constraints} \\

            \midrule
             Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\

             \makecell[r]{Abs. Max:} & 
            $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
               & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\
             \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\

            Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\

            Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}
        \end{tabular}
    \end{subtable} 
    \vspace{1em}
    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}

% \begin{table*}[t]
%     \centering
%     \footnotesize
%     \begin{subtable}[t!]{\textwidth}\centering
%         \begin{tabular}{c | c  c  c  c  c}
%         \multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} \\ $\,\,\interact(S_u ,S_v)$}}  & Sum & Absolute Maximum & Average & Maximum & Minimum \\
%  & $\displaystyle \sum_{e\in E_{uv}} \cost_e$  & $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$ & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big| $ &  $\displaystyle \max_{e\in E_{uv}} \cost_e$ & $\displaystyle \min_{e\in E_{uv}} \cost_e$ \\ \midrule

%             \thead{\textbf{Unsigned Graphs}} & \thead{Sum Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Average Linkage\\Hier. Aggl. Clust.} &\thead{Single Linkage\\Hier. Aggl. Clust.} &\thead{Complete Linkage\\Hier. Aggl. Clust.} \\
%             \thead{\textbf{Signed Graphs} \\\textbf{Without Constraints}} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
%             \thead{\textbf{Signed Graphs} \\\textbf{With Constraints}} & \thead{Greedy Fixation \cite{levinkov2017comparative}} & \thead{Mutex Watershed \cite{wolf2018mutex}} & \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} &  \thead{\textbf{NEW}} \\
%             % \multicolumn{2}{c|}{\multirow{2}{*}[-0.5em]{\thead{\textbf{\algname{} linkage criteria} $\,\,\interact(S_u ,S_v)$}}}  & \multirow{2}{*}[-0.5em]{\thead{\textbf{Unsigned Graphs}}} & \multicolumn{2}{c}{\thead{\textbf{Signed Graphs}}}  \\        
%             % \multicolumn{2}{c|}{} &  &  \multicolumn{1}{c}{\thead{No Constraints}} & \thead{With Constraints} \\ \midrule

%             %  Sum: & $\displaystyle \sum_{e\in E_{uv}} \cost_e$ & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{GAEC \cite{keuper2015efficient}} & \thead{Greedy\\Fixation \cite{levinkov2017comparative}} \\

%             %  \makecell[r]{Abs. Max:} & 
%             % $\displaystyle \cost_e$ with $\displaystyle e = \argmax_{t\in E_{uv}} |\cost_t|$
%             %    & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} & \thead{Mutex\\Watershed \cite{wolf2018mutex}} \\

%             %  \makecell[r]{Average:} & $\displaystyle \sum_{e\in E_{uv}} \cost_e \bigg/ \big|E_{uv}\big|  $ & \thead{ Average Linkage\\ Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\

%             % Max: & $\displaystyle \max_{e\in E_{uv}} \cost_e$ & \thead{Single Linkage\\Hier. Aggl. Clust.} & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}\\

%             % Min:& $\displaystyle \min_{e\in E_{uv}} \cost_e$ & \thead{Complete Linkage\\ Hier. Aggl. Clust.}  & \thead{\textbf{NEW}} & \thead{\textbf{NEW}}

%         \end{tabular}
%     \end{subtable} 
%     % \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
%     % \label{tab:linkage-criteria}
% \end{table*}

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. Only the \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
\label{fig:cremi_comparison}}
\end{figure*}

### 2020-03-10 chapters/5_experiments_cityscapes.tex
Update to ECCV template

>>>>

% \captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{figure}[t]
\centering
\begin{minipage}[t]{0.48 \textwidth}
\vspace{0pt}
\centering
\small
\begin{tabular}[t]{l|cc}
     Agglomeration method & AP \\ \midrule
    % PANet \cite{liu2018path} & - & \textbf{36.5} \\
    % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
      \textbf{\algname{} Average}& \textbf{34.3} \\
      \algname{} Average + Constraints & 33.9 \\
     MultiStepHAC \cite{liu2018affinity} & 33.0 \\
      \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
      \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
      \algname{} Sum \cite{keuper2015efficient} & 31.3 
\end{tabular}
\vspace*{1.5em}
\captionof{table}{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model trained in \cite{liu2018affinity} and different graph agglomeration methods.}
\label{tab:results_cityscapes_val}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\textwidth}
% \centering
\scriptsize
\begin{tabular}[t]{l|cc}
    \multirow{2}{*}{Method}    & AP  & AP 50\% \\ 
     & \multicolumn{2}{c}{(higher is better)} \\ \midrule
       Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
       UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
       SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
       AdaptIS \cite{sofiiuk2019adaptis} & 32.5 & 52.5 \\
       PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
       \textbf{GMIS\cite{liu2018affinity}+\algname{}Average} & \textbf{28.3} & \textbf{47.0} \\ 
       JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
       \textbf{GMIS} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
       Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
       SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
       % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
       % DWT \cite{bai2017deep} & 19.4 & 35.3 \\
       % InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
    \end{tabular}
% \caption{CityScapes \emph{test} set}
% \vspace*{0.6em}
\captionof{table}{Results on CityScapes test. Methods marked with~$\dagger$ are \emph{proposal-based}. Only methods that do not use external training data (such as MS COCO) are shown.}\label{tab:results_cityscapes}
\label{tab:results_cityscapes_test}
\end{minipage}
\end{figure}
\begin{figure}[t]
\centering
\begin{minipage}{\textwidth}
\centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_6.pdf} % left bottom right top
\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image from the \emph{validation} set.}\label{fig:cityscapes}
\end{minipage}
\end{figure}

### 2020-03-10 chapters/5_experiments_compare_rules.tex
Update to ECCV template

\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure*}
\centering
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    \end{subfigure}

        \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: $p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.46 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
}\label{fig:noise_plots}
\end{figure*}
\begin{figure*}[t]
        \centering
\begin{minipage}[t]{0.31\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         Method & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averaged over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.3\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
        Method & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
        \end{tabular}
        \vspace*{0.99em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (November 2019). All entries, apart from our using \algname{}, employ superpixel-based post-processing pipelines.}
    \label{tab:results_cremi_test}
\end{minipage}\hfill
\begin{minipage}[t]{0.35\textwidth}
\centering
    \scriptsize
    \vspace*{-1.5em}
\begin{tabular}[t]{l|cc}
        \multirow{2}{*}{Method}    & AP  & AP 50\% \\ 
         & \multicolumn{2}{c}{(higher is better)} \\ \midrule
           Panoptic-DeepLab \cite{cheng2019panopticdeeplab} & 34.6 & 57.3 \\
           UPSNet \cite{xiong2019upsnet} $\dagger$ & 33.0 & 59.6 \\
           SSAP \cite{Gao_2019_ICCV} & 32.7 & 51.8 \\
           AdaptIS \cite{sofiiuk2019adaptis} & 32.5 & 52.5 \\
           PANet \cite{liu2018path} $\dagger$ & 31.8 & 57.1 \\
           \textbf{GMIS Model \cite{liu2018affinity} + \algname{} Average} & \textbf{28.3} & \textbf{47.0} \\ 
           JOSECB \cite{neven2019instance} & 27.7 & 50.9 \\
           \textbf{GMIS} \cite{liu2018affinity} & \textbf{27.3} & \textbf{45.6} \\
           Mask R-CNN \cite{he2017mask} $\dagger$ & 26.2 & 49.9 \\
           SGN \cite{liu2017sgn} & 25.0 & 44.9 \\
           % DIN \cite{arnab2017pixelwise} & 20.0 & 38.8 \\
           % DWT \cite{bai2017deep} & 19.4 & 35.3 \\
           % InstanceCut \cite{kirillov2017instancecut} & 13.0 & 27.9 \\
        \end{tabular}
    % \caption{CityScapes \emph{test} set}
    % \vspace*{0.6em}
    \captionof{table}{Results on CityScapes test. Methods marked with~$\dagger$ are \emph{proposal-based}. Only methods that do not use external training data (such as MS COCO) are shown.}\label{tab:results_cityscapes}
    \label{tab:results_cityscapes_test}
\end{minipage}
\end{figure*}

\captionsetup[subtable]{labelformat=simple, labelsep=space, justification=centering, singlelinecheck=off}
\renewcommand*{\thesubtable}{(\alph{subtable})}
\begin{figure*}[t]
\begin{minipage}{0.65 \textwidth}
\centering
\includegraphics[width=\textwidth]{./figs/cityscapes_compare_6.pdf} % left bottom right top
\caption{Visual results given by different \algname{} linkage criteria on a crop of a CityScapes image from the \emph{validation} set.}\label{fig:cityscapes}
\end{minipage}\hfill
\begin{minipage}{0.3 \textwidth}
    \centering
    \small
        \begin{tabular}[t]{l|cc}
             Agglomeration method & AP \\ \midrule
            % PANet \cite{liu2018path} & - & \textbf{36.5} \\
            % Mask R-CNN \cite{he2017mask} & - & 31.5 \\ \hline
              \textbf{\algname{} Average}& \textbf{34.3} \\
              \algname{} Average + Constraints & 33.9 \\
             MultiStepHAC \cite{liu2018affinity} & 33.0 \\
              \algname{} Abs. Max. \cite{wolf2018mutex}  & 32.1 \\
              \algname{} Sum + Constraints  \cite{levinkov2017comparative} & 31.9  \\
              \algname{} Sum \cite{keuper2015efficient} & 31.3 \\
        \end{tabular}
    \vspace*{0.6em}
    \captionof{table}{Average Precision scores on CityScapes \emph{val} achieved by the GMIS Model trained in \cite{liu2018affinity} and different graph agglomeration methods.}
    \label{tab:results_cityscapes_val}
\end{minipage}
\end{figure*}

>>>>

\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure*}[t]
\centering
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_0.pdf}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/under_segment_plots_1.pdf}
    \end{subfigure}

        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_0.pdf}
        \caption{No long-range predictions: \\$p_{\mathrm{long}}=0$} \label{fig:merge_noise_only_direct}
    \end{subfigure} \hfill
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.1in 0.65in 0.45in,clip]{./figs/noise_plots/over_segment_plots_1.pdf}
        \caption{With long-range predictions: $p_{\mathrm{long}}=0.1$} \label{fig:merge_noise_with_long_range}
    \end{subfigure}
\caption{\algname{} sensitivity to noise: \emph{Average} linkage proved to be the most robust. Performances are given by Rand-Score (higher is better) depending on the amount of noise added to the CNN predictions. Solid lines represent median values over 30 experiments. Values between the 25th and the 75th percentile are shown in shaded areas. The two sets of experiments using under- and over-clustering noise are summarized in the plots at the top and at the bottom, respectively (see Appendix \ref{sec:appendix_noise_gen} for more details). For each experiment, some of the long-range CNN predictions were randomly selected with probability $p_{\mathrm{long}}$ and added as long-range edges to the pixel grid-graph. Experiments are performed on a crop of CREMI training sample B.
}\label{fig:noise_plots}
\end{figure*}
\begin{figure*}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         Method & \makecell{CREMI-Score \\(lower is better)} \\ \midrule 
\textbf{\algname{}} \textbf{Average}& \textbf{0.226}  \\
\algname{} Sum + Constraints \cite{levinkov2017comparative} & 0.282 \\
\algname{} Abs. Max. \cite{wolf2018mutex} & 0.322 \\
\algname{} Max. + Constraints & 0.324 \\
\algname{} Sum \cite{keuper2015efficient} & 0.334 \\
\algname{} Average + Constraints & 0.563 \\
THRESH & 1.521 \\ 
        \end{tabular}
    \captionof{table}{CREMI-Scores achieved by different linkage criteria and thresholding. All methods use the affinity predictions from our CNN as input. Scores are averaged over the three CREMI training datasets.}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
        Method & \makecell{CREMI-Score \\(lower is better)}  \\ \midrule
Our CNN + DTWS + LMC &  0.221\\
PNI CNN \cite{lee2017superhuman} & 0.228 \\
\textbf{Our CNN + \algname{} Average} & \textbf{0.241} \\
MALA CNN + MC \cite{funke2018large} & 0.276 \\
CRU-Net \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
        \end{tabular}
        \vspace*{0.99em}
    \captionof{table}{Current leading entries  in the CREMI challenge leaderboard \cite{cremiChallenge} (March 2020). All entries, apart from our using \algname{}, employ superpixel-based post-processing pipelines.}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure*}
